\textcolor{red}{Leveraging Machine Learning to Characterize Aquatic Environments with an Autonomous Team of Sensing Sentinels }

### 2024-01-09 paper/paper.tex

Each day over X terabytes of remote sensing data are collected fr

Context

Need

Task

Objective

@@

% https://gisgeography.com/hyperspectral-imaging/
% https://hyperspectral.azavea.com/
% https://sentinels.copernicus.eu/web/sentinel/user-guides/sentinel-1-sar/document-library/-/asset_publisher/1dO7RF5fJMbd/content/sentinel-high-level-operations-plan  <-- for amount of data produced by sentinel
The main areas of usage for hyperspectral imagery can be categorized into 8 groups. This includes vegetation, agriculture, geology, soil, water resources, disaster, and land use.

The underlying principle is that it improves any type of classification. For example, you can get more detail for geologic surface composition. The same is true for vegetation types, soil classes, and land cover too.

Hyperspectral imaging helps identify pests for crop management. Water resources are about understanding bathymetry, water quality, and chemistry. And it’s been used for disaster management such as prevention and post-monitoring

Step 1: Introduce your topic
Step 2: Describe the background
Step 3: Establish your research problem
Step 4: Specify your objective(s)
Step 5: Map out your paper

The introduction should answer three important questions:
1. What am I writing about?
2. Why is it important?
3. What do I want the reader to know about it?

Step 1: Establish a Territory
"In recent years..." or "researchers have become interested..."

Step 2: Establish a Niche
- Identify a gap that your research fills

@@

\\

@@

@@

The results of fitting our hyperparameter optimized models are listed in Table~\ref{tab:fit-results}. For each model, the $R^2$, RMSE, and MAE were evaluated using 10-fold cross validation. We observe considerable

\begin{table}[H]
  \caption{Summary of fitting statistics for each target measurement. Values were evaluated using 10-fold cross validation on the training set. The estimated uncertainty is evaluated using conformal prediction so that a prediction $\hat{y}\pm \Delta y$ achieves 90\% coverage on the validation holdout set. The empirical coverage is the percentage of predictions in the holdout testing set that fall within the confidence interval determined by conformal prediction. \label{tab:fit-results}}
  \begin{adjustwidth}{-\extralength}{0cm}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \begin{tabularx}{\fulllength}{CCCCCC}
    \toprule
    \textbf{Target (units)} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)}\\
    \midrule
    Temperature (°C) & 0.999 ± 5.1e-5 & 0.0546 ± 0.0022 & 0.0316 ± 0.0015 & ± 0.084 & 89.7\\
    \midrule
    Conductivity ($\mu$S/cm) & 0.999 ± 0.00011 & 0.888 ± 0.067 & 0.497 ± 0.025 & ± 1.3 & 91.5\\
    \midrule
    $\mathrm{Ca}^{2+}$ (mg/l) & 0.999 ± 0.00031 & 0.544 ± 0.058 & 0.267 ± 0.013 & ± 0.72 & 89.9\\
    \midrule
    Dissolved Oxygen (mg/l) & 0.998 ± 0.00015 & 0.0931 ± 0.004 & 0.055 ± 0.0022 & ± 0.14 & 88.5\\
    \midrule
    Salinity (PSS) & 0.995 ± 0.00061 & 0.00124 ± 6.2e-5 & 0.000432 ± 2.6e-5 & ± 0.0009 & 90.1\\
    \midrule
    Tryptophan (ppb) & 0.989 ± 0.0046 & 0.206 ± 0.046 & 0.117 ± 0.0085 & ± 0.28 & 89.0\\
    \midrule
    pH & 0.988 ± 0.0018 & 0.0232 ± 0.0019 & 0.0119 ± 0.00045 & ± 0.032 & 92.5\\
    \midrule
    $\mathrm{Na^+} (mg/l)$ & 0.982 ± 0.0034 & 9.01 ± 0.88 & 4.17 ± 0.22 & ± 11.0 & 90.8\\
    \midrule
    $\mathrm{Cl^-}$ (mg/l) & 0.982 ± 0.0054 & 1.96 ± 0.28 & 1.0 ± 0.066 & ± 2.3 & 89.7\\
    \midrule
    Blue-Green Algae [Phycoerythrin] (ppb) & 0.939 ± 0.017 & 3.12 ± 0.43 & 0.84 ± 0.065 & ± 1.8 & 91.4\\
    \midrule
    CDOM (ppb) & 0.934 ± 0.02 & 0.58 ± 0.093 & 0.219 ± 0.013 & ± 0.46 & 90.3\\
    \midrule
    Optical Brighteners (ppb) & 0.920 ± 0.015 & 0.11 ± 0.0092 & 0.0617 ± 0.0019 & ± 0.13 & 92.4\\
    \midrule
    $\mathrm{NO_3^-} (mg/l-N)$ & 0.890 ± 0.013 & 0.0575 ± 0.0036 & 0.0353 ± 0.00091 & ± 0.079 & 90.7\\
    \midrule
    Crude Oil (ppb) & 0.890 ± 0.037 & 0.55 ± 0.11 & 0.174 ± 0.019 & ± 0.3 & 89.2\\
    \midrule
    Chlorophyll A with Red Excitation ($\mu$g/l) & 0.728 ± 0.11 & 94.9 ± 37.0 & 17.0 ± 2.5 &  ± 31.0 & 91.1\\
    \midrule
    Chlorophyll A ($\mu$g/l) & 0.672 ± 0.17 & 1.96 ± 0.25 & 0.482 ± 0.044 &  ± 0.83 & 90.6\\
    \midrule
    Turbidity (FNU) & 0.616 ± 0.19 & 52.6 ± 23.0 & 7.62 ± 2.2 & ± 9.2 & 87.9\\
    \bottomrule
  \end{tabularx}
  \end{adjustwidth}
\end{table}

@@

\subsection{Chemicals-of-Concern}

@@

@@

>>>>

Each day over X terabytes of remote sensing data are collected from...

@@

@@

@@

- optically significant substances (OSS)
- Colored dissolved organic matter (CDOM, also known as yellow substances, humic matter or gelbstoff) includes compounds produced during the decay of plant matter
- Estimates concentrations of Chlorophyll-a, Total Suspended Solids, and the absorption coefficient of CDOM $a_{CDOM}(400)$ using Medium Resolution Imaging Spectrometer (MERIS) data during bloom in Gulf of Finland. They do this using band-ratio algorithms \cite{remote-sensing-finland}.
-  We should note that band-ratio algroithms are impacted by atmospheric factors like the in-column aerosol distribution.
- The amounts of aerosols (dust, haze, etc) and gases (ozone, water vapor, etc) present in the atmosphere vary spatially and temporally. These variations impact the estimation of water quality characteristics via remote sensing methods \cite{remote-sensing-finland}
- However, when data from different dates and locations are compared and atmospheric correction is necessary \cite{remote-sensing-finland}.

- Used a support vector machine (SVM) to classify hyperspectral images of vegetation acquired by a UAV and produced a high-resolution classification map \cite{uav-hsi-classification}.
- Large misclassification occured in shaded areas

For example, Garcia -Ruiz et al. (2013) conducted a UAV-based 56 aerial survey with multispectral cameras over a citrus orchard, and found that 57 UAV-based datasets yielded better classification accuracy than aircraft-based 58 datasets for diseased citrus trees. Moreover, Peña et al. (2013, 2015) applied 59 UAV-based multispectral imaging for the early detection of weed seedlings in 60 combination with object-based image analysis.

@@

The results of fitting our hyperparameter optimized models are listed in Table~\ref{tab:fit-results}. For each model, the $R^2$, RMSE, and MAE were evaluated using 6-fold cross validation. We observe considerable

\begin{table}[H]
  \caption{Summary of fitting statistics for each target measurement. Models were evaluated using 6-fold cross validation on the training set. The estimated uncertainty is evaluated using conformal prediction so that a prediction $\hat{y}\pm \Delta y$ achieves 90\% coverage on the calibration holdout set. The empirical coverage is the percentage of predictions in the testing set that fall within the confidence interval determined by conformal prediction. \label{tab:fit-results}}
  \begin{adjustwidth}{-\extralength}{0cm}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \begin{tabularx}{\fulllength}{CCCCCC}
    \toprule
    \textbf{Target (units)} & \textbf{$\text{R}^2$} & \textbf{RMSE} & \textbf{MAE} & \textbf{Estimated Uncertainty} & \textbf{Empirical Coverage (\%)}\\
    \midrule
    Temperature (°C) & 1.0 ± 1.98e-5 & 0.0398 ± 0.00096 & 0.0267 ± 0.00055 &  ± 0.061 & 89.8\\
    \midrule
    Conductivity ($\mu$S/cm) & 0.999 ± 2.17e-5 & 0.853 ± 0.0114 & 0.55 ± 0.00564 &  ± 1.3 & 89.8\\
    \midrule
    $\mathrm{Ca}^{2+}$ (mg/l) & 0.999 ± 3.53e-5 & 0.423 ± 0.0101 & 0.243 ± 0.00552 &  ± 0.59 & 89.7\\
    \midrule
    Dissolved Oxygen (mg/l) & 0.999 ± 3.17e-5 & 0.0705 ± 0.000984 & 0.0467 ± 0.000418 &  ± 0.11 & 89.8\\
    \midrule
    Salinity (PSU) & 0.998 ± 0.000129 & 0.000759 ± 1.8e-5 & 0.000265 ± 6.1e-6 &  ± 0.00051 & 89.6\\
    \midrule
    $\mathrm{Cl^-}$ (mg/l) & 0.994 ± 0.000441 & 1.15 ± 0.0418 & 0.578 ± 0.00534 &  ± 1.4 & 90.3\\
    \midrule
    $\mathrm{Na^+} (mg/l)$ & 0.992 ± 0.000309 & 6.17 ± 0.134 & 2.85 ± 0.0536 &  ± 7.2 & 89.9\\
    \midrule
    Tryptophan (ppb) & 0.991 ± 0.00038 & 0.188 ± 0.00404 & 0.112 ± 0.00149 &  ± 0.26 & 89.9\\
    \midrule
    pH & 0.991 ± 0.000327 & 0.0177 ± 0.000295 & 0.0109 ± 6.56e-5 &  ± 0.024 & 89.9\\
    \midrule
    Blue-Green Algae [Phycoerythrin] (ppb) & 0.981 ± 0.00186 & 1.72 ± 0.0947 & 0.608 ± 0.0218 &  ± 1.4 & 90.2\\
    \midrule
    $\mathrm{NO_3^-} (mg/l-N)$ & 0.968 ± 0.00203 & 0.0308 ± 0.00113 & 0.0146 ± 0.000256 &  ± 0.043 & 89.9\\
    \midrule
    CDOM (ppb) & 0.966 ± 0.00228 & 0.464 ± 0.0195 & 0.144 ± 0.00449 &  ± 0.22 & 89.3\\
    \midrule
    Chlorophyll A ($\mu$g/l) & 0.924 ± 0.00645 & 1.29 ± 0.0667 & 0.359 ± 0.0079 &  ± 0.73 & 90.2\\
    \midrule
    Optical Brighteners (ppb) & 0.915 ± 0.00406 & 0.118 ± 0.00169 & 0.0568 ± 0.000218 &  ± 0.1 & 89.8\\
    \midrule
    Chlorophyll A with Red Excitation ($\mu$g/l) & 0.909 ± 0.00794 & 77.6 ± 3.91 & 15.6 ± 0.418 &  ± 25.0 & 90.5\\
    \midrule
    Crude Oil (ppb) & 0.906 ± 0.00606 & 0.588 ± 0.019 & 0.162 ± 0.00234 &  ± 0.23 & 89.7\\
    \midrule
    Turbidity (FNU) & 0.812 ± 0.0158 & 60.2 ± 2.61 & 6.98 ± 0.431 &  ± 3.4 & 89.5\\
    \bottomrule
  \end{tabularx}
  \end{adjustwidth}
\end{table}

@@

\subsection{Biochemical Measurements}

@@

\begin{figure}[H]
\includegraphics[width=10.5 cm]{paper/figures/results/downwelling-hist.pdf}
\caption{Distribution of total downwelling intensity during each of the three HSI collection flights. The multi-modal nature of these distributions reflects the impact of the relative orientation of the drone to the sun as well as potential occlusion due to the presence of clouds.\label{fig:downwelling-hist}}
\end{figure}

@@

\subsection{Extensions and Next Steps}

The current implementation of conformal prediction utilized in these models estimates a fixed width confidence interval for all outputs. This could be improved by training a secondary \textit{residual} model on the errors produced by the base learner, that is, a model which predicts 
\begin{equation}
    r(X) = \lvert f(X) - y \rvert = \lvert \hat{y} - y \rvert.
\end{equation}
In the conformal prediction framework, such a model could then be used to produce \textit{adaptive} uncertainty estimates using the augmented heuristic function
\begin{equation}
    S(X,y)  = \dfrac{\lvert \hat{y} - y \rvert }{r(X)}
\end{equation}
to produce scores on the calibration holdout set. With access to adaptive uncertainty estimates, we can then augment the navigation control for the USV to encourage data collection in regions of high model uncertainty. This would further optimize the data collection and calibration procedure at the expense of increased model training times.
